ms_results

### 2023-01-06 ms_figures.Rmd
ms manuscript changes

```{r set_directories}
# Set time series dates
date_nodash <- "20220926"
date_dash <- "2022-09-26"

# Set directories 
outdir <- "/Volumes/jgephart/ARTIS/Outputs/ms_seafood_globalization"

@@

# Create basic plot for the legend
artis_region_method %>%
  group_by(year, exporter_region) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  ggplot(aes(x = year, y = live_weight_t, fill = exporter_region)) +
  geom_area() +
  scale_fill_manual(values = region_colors) +
  labs(fill = "Region") +
  theme(legend.position = "bottom")
```

@@

@@

global_percap_supply_line <- supply_total %>%
  filter(region != "Other nei") %>%
  group_by(year, habitat_method) %>%
  summarise(supply_per_cap = (sum(supply_no_error))/sum(pop)) %>%
  ggplot(aes(x = year, y = supply_per_cap, color = habitat_method)) +
  geom_line() + 
  labs(y = "Per capita supply (kg)", x = "", color = "Source") +
  scale_color_manual(values = habitat_source_colors) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

```{r}
# Plot relationship between per capita supply and imports by prod source and region
country_supply <- supply %>% 
  filter(year == 2018, region != "Other nei") %>% 
  group_by(iso3c, region, year) %>% 
  summarise(supply = sum(supply),
            supply_no_error = sum(supply_no_error),
            supply_domestic = sum(supply_domestic),
            supply_foreign = sum(supply_foreign),
            import = sum(imports_live_weight_t), 
            domestic_export = sum(domestic_export),
            foreign_export = sum(foreign_export),
            error_export = sum(error_export), 
            production_t = sum(production_t)
  ) %>% 
  left_join(pop %>% select(-region), by = c("iso3c", "year")) %>%
  mutate(supply_per_cap = supply_no_error/pop) 
```

```{r, fig.height = 5, fig.width = 3}
country_supply %>% 
  ungroup() %>%
  mutate(iso3c = fct_reorder(iso3c, supply_per_cap)) %>%
  filter(supply_per_cap > 50) %>%
  ggplot(aes(x = supply_per_cap, y = iso3c, fill = region)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = region_colors) +
  theme_bw() +
  theme(legend.position = "none")

@@

```{r, fig.height = 4, fig.width = 5}
# Join figures
png("outputs/fig3.png")
ggarrange(
  ggarrange(global_percap_supply_line, regional_percap_supply_area, 
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("a", "b")),
  ggarrange(global_supply_trends, region_supply_trends,
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("c", "d")),
  ggarrange(import_supply, export_supply, 
            common.legend = TRUE, nrow = 1, widths = c(1, 1),
            labels = c("e", "f")),
  nrow = 3
)
dev.off()
```

>>>>

```{r set_directories}
# Set directories 
outdir <- "/Volumes/jgephart/ARTIS/Outputs/ms_seafood_globalization"
outdir <- "outputs"

@@

# Create basic plot for the legend
artis_region_method %>%
  group_by(year, exporter_region) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  ggplot(aes(x = year, y = live_weight_t, fill = exporter_region)) +
  geom_area() +
  scale_fill_manual(values = region_colors) +
  labs(fill = "Region") +
  theme(legend.position = "bottom") +
  theme_bw()
```

@@

write.csv(supply, file.path(outdir, "supply.csv"), row.names = FALSE)
```

@@

global_percap_supply_line <- supply_total %>%
  filter(region != "Other nei") %>%
  group_by(year, habitat_method) %>%
  summarise(supply_per_cap = 1000 * (sum(supply_no_error))/sum(pop)) %>%
  ggplot(aes(x = year, y = supply_per_cap, color = habitat_method)) +
  geom_line() + 
  labs(y = "Per capita supply (kg)", x = "", color = "Source") +
  scale_color_manual(values = habitat_source_colors) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

```{r}
# Plot relationship between per capita supply and imports by prod source and region
country_supply <- supply %>% 
  filter(year == 2018, region != "Other nei") %>% 
  group_by(iso3c, region, year) %>% 
  summarise(supply = sum(supply),
            supply_no_error = sum(supply_no_error),
            supply_domestic = sum(supply_domestic),
            supply_foreign = sum(supply_foreign),
            import = sum(imports_live_weight_t), 
            domestic_export = sum(domestic_export),
            foreign_export = sum(foreign_export),
            error_export = sum(error_export), 
            production_t = sum(production_t)
  ) %>% 
  left_join(pop %>% select(-region), by = c("iso3c", "year")) %>%
  mutate(supply_per_cap = supply_no_error/pop) %>%
  # Converting from tonnes to kg
  mutate(supply_per_cap = 1000 * supply_per_cap)
```

```{r, fig.height = 5, fig.width = 3}
country_supply %>% 
  ungroup() %>%
  mutate(iso3c = fct_reorder(iso3c, supply_per_cap)) %>%
  #filter(supply_per_cap > 50) %>%
  ggplot(aes(x = supply_per_cap, y = iso3c, fill = region)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = region_colors) +
  theme_bw() +
  theme(legend.position = "none")

@@

```{r, fig.height = 4, fig.width = 5}
# Join figures
png("outputs/fig3.png")
ggarrange(
  ggarrange(global_percap_supply_line, regional_percap_supply_area, 
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("a", "b")),
  ggarrange(global_supply_trends, region_supply_trends,
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("c", "d")),
  # ggarrange(import_supply, export_supply, 
  #           common.legend = TRUE, nrow = 1, widths = c(1, 1),
  #           labels = c("e", "f")),
  nrow = 3
)
dev.off()
```

### 2023-01-06 ms_results.Rmd
ms manuscript changes

# Load packages
library(tidyverse)
library(countrycode)
library(kableExtra)
library(ggpubr)

@@

```{r covid_effect}
artis %>% 
  filter(year %in% 2019:2020) %>% 
  group_by(year, habitat_method) %>% 
  summarise(live_weight_t = sum(live_weight_t)) %>% 
  pivot_wider(names_from = year, values_from = live_weight_t, names_prefix = "year") %>% 
  mutate(change = (year2019-year2020)/year2020) %>% 
  arrange(desc(change))
```

@@

@@

Globally, blue food consumption increased from X in 1996 to Y in 2020. Blue food consumption also increased across all regions outside of South America, where per capita blue food consumption decreased X%, from X% in 1996 to Y% in 2020. [Double check that FMFO was excluded and discuss this pattern]. Most of the global increase was from inland and marine aquaculture, which increased by X and Y%, respectively, over that period while marine capture consumption declined by X%. Marine capture still makes up X% of global blue food consumption and its contribution to regional blue food supplies ranges from X% in Y to X% in Asia, where farmed consumption overtook wild consumption in [year].

High reliance on foreign-sourced foods can pose a food security risk, motivating policies to protect domestic supplies such as the development of grain stocks and support for domestic food production (REFs). For example, high seafood import dependence in the US was used to propose a suite of policy changes to boost domestic production, including expanding aquaculture production and opening marine protected areas to fishing (Gephart et al. 2019). Since we estimate exports from domestic and foreign sources, we are able to track changes in reliance on foreign sourced products. Globally, the share of consumption that is foreign sourced has increased from X% to Y% (Fig 3c), but patterns vary across regions with Asia and S America dominated by domestic supply, but Europe dominated by foreign supply (Fig 3d). [Add points about patterns across production methods].

>>>>

# Load packages
library(tidyverse)
library(countrycode)
library(kableExtra)
library(ggpubr)
library(tidytext)

@@

```{r covid_effect}
# artis %>% 
#   filter(year %in% 2019:2020) %>% 
#   group_by(year, habitat_method) %>% 
#   summarise(live_weight_t = sum(live_weight_t)) %>% 
#   pivot_wider(names_from = year, values_from = live_weight_t, names_prefix = "year") %>% 
#   mutate(change = (year2019-year2020)/year2020) %>% 
#   arrange(desc(change))
```

@@

```{r consumption}

supply <- read.csv("outputs/supply.csv")

global_supply <- supply %>%
  group_by(year) %>%
  summarize(supply_no_error = sum(supply_no_error) / 1000000) %>%
  ungroup()

global_supply_1996 <- global_supply %>%
  filter(year == 1996) %>%
  pull(supply_no_error)

global_supply_2020 <- global_supply %>%
  filter(year == 2020) %>%
  pull(supply_no_error)

regional_supply <- supply %>%
  group_by(year, region) %>%
  summarize(supply_no_error = sum(supply_no_error)) %>%
  ungroup() %>%
  group_by(year) %>%
  mutate(supply_no_error_total = sum(supply_no_error)) %>%
  ungroup() %>%
  mutate(percent_supply = 100 * supply_no_error / supply_no_error_total)

habitat_method_supply <- supply %>%
  group_by(year, habitat, method) %>%
  summarize(supply_no_error = sum(supply_no_error)) %>%
  ungroup() %>%
  group_by(year) %>%
  mutate(supply_no_error_total = sum(supply_no_error)) %>%
  ungroup() %>%
  mutate(percent_supply = 100 * supply_no_error / supply_no_error_total)

tmp <- habitat_method_supply %>%
  select(habitat, method, year, supply_no_error) %>%
  filter(year == 1996 | year == 2020) %>%
  mutate(year = paste("year", year, sep = "_")) %>%
  pivot_wider(names_from = year, values_from = supply_no_error) %>%
  mutate(percent_diff = 100 * (year_2020 - year_1996) / year_1996)

inland_aqua_supply_change <- tmp %>%
  filter(habitat == "inland" & method == "aquaculture") %>%
  pull(percent_diff)

marine_aqua_supply_change <- tmp %>%
  filter(habitat == "marine" & method == "aquaculture") %>%
  pull(percent_diff)

marine_cap_supply_change <- tmp %>%
  filter(habitat == "marine" & method == "capture") %>%
  mutate(percent_diff = abs(percent_diff)) %>%
  pull(percent_diff)

marine_cap_supply_percent <- habitat_method_supply %>%
  filter(year == 2020) %>%
  filter(percent_supply == max(percent_supply)) %>%
  pull(percent_supply)

method_supplies <- supply %>%
  filter(year == 2020) %>%
  group_by(method) %>%
  summarize(supply_no_error = sum(supply_no_error)) %>%
  ungroup() %>%
  mutate(total_supply = sum(supply_no_error)) %>%
  mutate(percent_supply = 100 * supply_no_error / total_supply)

regional_method_supplies <- supply %>%
  filter(year == 2020) %>%
  group_by(year, region, method) %>%
  summarize(supply_no_error = sum(supply_no_error)) %>%
  ungroup() %>%
  group_by(year, region) %>%
  mutate(region_supply = sum(supply_no_error)) %>%
  ungroup() %>%
  mutate(percent_supply = 100 * supply_no_error / region_supply) %>%
  select(region, region_supply, method, percent_supply) %>%
  pivot_wider(names_from = "method", values_from = "percent_supply")

oceania_cap_supply_percent <- regional_method_supplies %>%
  filter(region == "Oceania") %>%
  pull(capture)

asia_cap_supply_percent <- regional_method_supplies %>%
  filter(region == "Asia") %>%
  pull(capture)

cap_supply_percent <- method_supplies %>%
  filter(method == "capture") %>%
  pull(percent_supply)

asia_farmed_year <- supply %>%
  filter(region == "Asia") %>%
  group_by(year, method) %>%
  summarize(supply_no_error = sum(supply_no_error)) %>%
  ungroup() %>%
  filter(method == "capture" | method == "aquaculture") %>%
  pivot_wider(names_from = method, values_from = supply_no_error) %>%
  filter(aquaculture > capture) %>%
  filter(year == min(year)) %>%
  pull(year)

consumption_foreign <- supply %>%
  filter(year == 1996 | year == 2020) %>%
  group_by(year) %>%
  summarize(supply_foreign = sum(supply_foreign),
            supply_no_error = sum(supply_no_error)) %>%
  ungroup() %>%
  mutate(percent_supply = 100 * supply_foreign / supply_no_error)

foreign_consumption_start <- consumption_foreign %>%
  filter(year == 1996) %>%
  pull(percent_supply)

foreign_consumption_end <- consumption_foreign %>%
  filter(year == 2020) %>%
  pull(percent_supply)

@@

Globally, blue food consumption increased from `r signif(global_supply_1996, digit = 3)` (million tonnes) in 1996 to `r signif(global_supply_2020, digit = 3)` (million tonnes) in 2020. Blue food consumption also increased across all regions outside of South America, where per capita blue food consumption decreased X%, from X% in 1996 to Y% in 2020. [say this is supply included non food uses] [Double check that FMFO was excluded and discuss this pattern]. Most of the global increase was from inland and marine aquaculture, which increased by `r signif(inland_aqua_supply_change, digits = 3)` and `r signif(inland_aqua_supply_change, digits = 3)`%, respectively, over that period while marine capture consumption declined by `r signif(marine_cap_supply_change, digits = 1)`%. Capture still makes up `r signif(cap_supply_percent, digits = 2)`% of global blue food consumption and its contribution to regional blue food supplies ranges from `r signif(oceania_cap_supply_percent, digits = 2)`% in Oceania to `r signif(asia_cap_supply_percent, digits = 2)`% in Asia, where farmed consumption overtook wild consumption in `r asia_farmed_year`.

High reliance on foreign-sourced foods can pose a food security risk, motivating policies to protect domestic supplies such as the development of grain stocks and support for domestic food production (REFs). For example, high seafood import dependence in the US was used to propose a suite of policy changes to boost domestic production, including expanding aquaculture production and opening marine protected areas to fishing (Gephart et al. 2019). Since we estimate exports from domestic and foreign sources, we are able to track changes in reliance on foreign sourced products. Globally, the share of consumption that is foreign sourced has increased from `r signif(foreign_consumption_start, digits = 3)`% to `r signif(foreign_consumption_end, digits = 3)`% (Fig 3c), but patterns vary across regions with Asia and S America dominated by domestic supply, but Europe dominated by foreign supply (Fig 3d). [Add points about patterns across production methods].
